Multi-target detection and clustering with application to cryo-electron microscopy

### 2019-02-14 inverse_problems/inverse_problems.tex
Added red dots to figure KL-XP and included in the paper with caption.

\usepackage[margin=.6in]{geometry}

@@

\subsection{Equivalence between the autocorrelations of under the separation and the Poisson process} \label{sec:poisson}

@@

\TODO{Probably should be re-written}
Clearly, the first-order autocorrelation provides us one equation. For second-order autocorrelations, notice  that $a_y^2[\ell]$ suffers no noise-induced bias for $\ell$ in $1$ to $L-1$. Thus if $\sigma$ is known we obtain $L$ equations, while if not we omit $\ell = 0$. This has the practical effect that we need not know $\sigma$ to make sense of the computed quantities, while loosing one one equation. 
Likewise, for third-order autocorrelations, $a_y^3[\ell_1, \ell_2]$ for $0 \leq \ell_1, \ell_2 \leq L-1$ such that $\ell_2 \leq \ell_1$ includes all relevant entries for our purpose (this accounts for symmetries): $\frac{(L+1)(L+2)}{2}-2$ in total. 
If we further exclude any such that $\ell_1, \ell_2$ or $\ell_1 - \ell_2$ are zero to avoid the need to estimate $\sigma$---there are $\frac{(L-1)(L-2)}{2}$ remaining entries. 
Hence, if $\sigma$ is know we have 
\begin{align*}
1 + L + \frac{(L+1)(L+2)}{2}-2 = \frac{1}{2} L (L+5)
\end{align*}
and if it unknown
\begin{align*}
1 + (L-1) + \frac{(L-1)(L-2)}{2} = \frac{1}{2} L (L-1) + 1
\end{align*}
coefficients in total. Since we aim to estimate $KL$ parameters (for the $K$ signals of length $L$) plus $K$ parameters (for the densities $\gamma_k$), an absolute upper bound on $K$  is
\begin{equation}
K\leq \frac{L(L+5)}{2(L+1)},
\end{equation}
\begin{align*}
K \leq \frac{ L (L-1) + 1}{2(L+1)}.
\end{align*}
Thus, we conjecture that approximately $L/2$ signals can be decomposed from  the first three mixed autocorrelations.

@@

>>>>

\usepackage[margin=3cm]{geometry}

@@

\subsection{Equivalence between the autocorrelations of under the separation and the Poisson process \TODO{?}} \label{sec:poisson}

@@

\TODO{Probably should be re-written}
Clearly, the first-order autocorrelation provides us one equation. For second-order autocorrelations, notice  that $a_y^2[\ell]$ suffers no noise-induced bias for $\ell$ in $1$ to $L-1$. Thus if $\sigma$ is known we obtain $L$ equations, while if not we omit $\ell = 0$. This has the practical effect that we need not know $\sigma$ to make sense of the computed quantities, while loosing one one equation. 
Likewise, for third-order autocorrelations, $a_y^3[\ell_1, \ell_2]$ for $0 \leq \ell_1, \ell_2 \leq L-1$ such that $\ell_2 \leq \ell_1$ includes all relevant entries for our purpose (this accounts for symmetries): $\frac{(L+1)(L+2)}{2}-2$ in total. 
If we further exclude any such that $\ell_1, \ell_2$ or $\ell_1 - \ell_2$ are zero to avoid the need to estimate $\sigma$---there are $\frac{(L-1)(L-2)}{2}$ remaining entries. 
Hence, if $\sigma$ is known we have 
\begin{align*}
1 + L + \frac{(L+1)(L+2)}{2}-2 = \frac{1}{2} L (L+5)
\end{align*}
and if it unknown
\begin{align*}
1 + (L-1) + \frac{(L-1)(L-2)}{2} = \frac{1}{2} L (L-1) + 1
\end{align*}
coefficients in total. Since we aim to estimate $KL$ parameters (for the $K$ signals of length $L$) plus $K$ parameters (for the densities $\gamma_k$), an absolute upper bound on $K$  is
\begin{equation}
K\leq \frac{L(L+5)}{2(L+1)},
\end{equation}
\begin{align*}
K \leq \frac{ L (L-1) + 1}{2(L+1)}.
\end{align*}
Thus, we conjecture that approximately $L/2$ signals can be decomposed from  the first three mixed autocorrelations.

@@

\begin{figure}[t]
	\centering
	\includegraphics[width=.7\linewidth]{KLXP/XP1}
	\caption{In the $N \to \infty$ regime (access to exact moments, excluding biased entries) and with known uniform densities, it seems $K$ up to $\sqrt{L}$ (red curve) i.i.d.\ Gaussian signals of length $L$ can be recovered from the known moments. CPU time in seconds. Strictly above red dots, recovery is impossible because the number of unknowns exceeds the number of computed moments. Similar to~\cite[Fig.~4.1]{boumal2017heterogeneous}, this experiment suggests a possible statistical-computational gap.}
	\label{fig:KLXP}
\end{figure}
